An event-sourced and distributed database with IPLD and materialized views

### 2019-09-20 draft.tex
updates: more updates
Signed-off-by: Carson Farmer <carson.farmer@gmail.com>

Cryptographically linked events can also represent a clock. One such example is called the Merkle-Clock \cite{sanjuanMerkleCRDTs2019}. The Merkle-Clock relies on properties of a Merkle-DAG to provide strict partial ordering between events, which has limitations \cite[sec. 4.3]{sanjuanMerkleCRDTs2019}:

@@

See Section \ref{sec:merkleclocks}.

@@

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses (see Example \ref{ex:Multiaddress}).

In practice, to reach a Log via it's IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress (see Example \ref{ex:Multiaddress}).

@@

MISSING PEER ADDRESS BOOK?

>>>>

Cryptographically linked events can also represent a clock (See Section \ref{sec:merkleclocks}). One such example is called the Merkle-Clock \cite{sanjuanMerkleCRDTs2019}. The Merkle-Clock relies on properties of a Merkle-DAG to provide strict partial ordering between events, which has limitations \cite[sec. 4.3]{sanjuanMerkleCRDTs2019}:

@@

@@

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses\cite{Multiaddr}. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses. To reach a Log via it's IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress (see Example \ref{ex:Multiaddress}).

@@
